---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color: #f9f9f9;
  color: #333;
  font-family: 'Helvetica Neue', Helvetica, Arial, sans-serif;
  line-height: 1.6;
  padding: 20px;
  margin: 0 auto;
  max-width: 800px;
  text-align: center; /* Center-align all text */
}

h1, h2, h3 {
  color: #2c3e50;
  margin-bottom: 15px;
}

h1 {
  border-bottom: 2px solid #e0e0e0;
  padding-bottom: 10px;
}

p {
  margin-bottom: 15px;
}

.figure {
  margin-bottom: 40px;
}

```

## What's going on with this data?
Our dynamic report provides an analysis on push-up performance by tracking completed push-ups through google forms. In this dynamic report, we will presenting our data through bar charts and summary statistics of push-up types, push-ups completed and difficulty of push-ups.

## Bar Graphs

```{r}
pets <- c("cat", "dog", "turtle", "rabbit")
best_pet <- pets[1]

library(tidyverse)

#loading data from csv
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTCuyM3zBoKPSOjDOWMaCjzQbdgbmzHHZjBpi9RwOn5DQaztop3olqnd6eyCf5HyZrSTXnKakWQPARs/pub?output=csv")

#renaming data
latest_data <- logged_data %>%
  rename(Time = 1,
         Date = 2,
         Type = 3,
         Count = 4,
         Difficulty = 5)

#getting data from table
pushup_count <- latest_data$Count
difficulty <- latest_data$Difficulty

#summary values
max_pushup <- max(pushup_count)
min_pushup <- min(pushup_count)
pushup_avg <- mean(pushup_count) %>% round(1)
avg_diff <- mean(difficulty) %>% round(1)

#getting average pushups completed
average_data <- latest_data %>%
  group_by(Type) %>%
  summarise(avg_pushups = mean(Count, na.rm = TRUE))

#create bar charts

ggplot(average_data) +
  geom_col(aes(x = Type, y = avg_pushups)) +
  labs(title = "Average Number of Pushups by Type",
       x = "Type of Pushup",
       y = "Average Number of Pushups")

ggplot(latest_data) +
  geom_bar(aes(x = Difficulty)) +
  labs(title = "Distribution of Difficulty Ratings", 
       x = "Diffuculty Rating", y = "Count")

ggplot(latest_data) +
  geom_bar(aes(x = Type)) +
  labs(title = "Distribution of Types of Push-ups", 
       x = "Types of Push-ups", y = "Count")
  

```

## Summary
The most amount of push-ups completed is `r max_pushup` push-ups.    
The least amount of push-ups completed is `r min_pushup` push-ups.  
The average amount of push-ups completed is `r pushup_avg` push-ups.  
The average effort rating of the push-ups is `r avg_diff`.  
